\chapter*{Acknowledgments\markboth{Acknowledgements}{Acknowledgments}}
\thispagestyle{empty}
\addcontentsline{toc}{chapter}{Acknowledgments}
\onehalfspacing\label{chap:Acknowledgements}
\noindent Elli, thank you for giving me the opportunity to complete my PhD studies under your supervision. Thank you for always being available to answer the many questions and for always having interesting project ideas to pursue. During my time at DESY I was able to collaborate with Alessandro Pini and Michelangelo Preti, whom I thank for many engaging and interesting discussions. I would also like to thank Pedro Liendo and Madelena Lemos for always being willing to explain and discuss things with me. 
I would also like to give special thanks to Alessandro Pini, Troy Figiel, Philipp Tontsch and Jan Makkinje for reading various parts of this thesis and for providing feedback. Extra thanks also to Philipp for translating the abstract.\newline

\noindent My work was supported by the German Research Foundation (DFG) via the Emmy Noether program `Exact results in Gauge theories'.\newline

\noindent I would like to thank my friends Alessandro, Giovanni, Ilija, Ioana, Ivan, Jan Peter, Michelangelo, Rob, Seva, Troy and Yannick for their friendship and for sharing many enjoyable times over the past three years. To Jan, thank you for inviting me to visit you in Boston it was a great time and I look forward to our road trip soon. Troy, we started our PhD's together and you were really the first person that I got to know in Hamburg. I'm so grateful to have had a person with whom I can always talk to, be it about mathematics or otherwise, and I'm happy to call you my closest friend.\newline

\noindent Flavia, you make me feel so happy every moment that we spend together. You are smart and kind and thoughtful. You always make me smile and laugh and I feel that I can always talk about  anything with you. You make me feel special and I love that you encourage me to try new things and the way that you always enjoy life to the fullest. \newline

\noindent I am very grateful to all of my family for all of their unconditional support. To my parents, Gill and Phil, without you this would not have been possible. You have always supported, encouraged and believed in me throughout everything. To my brother, Dan, I am pleased that even if we are separated by a country we still are and always will be best friends. To Nan, thank you for always believing in me and encouraging me to pursue my dreams. To Jane, Jill and Vanessa thank you for all of your love and encouragement.


\newpage

\newpage
\thispagestyle{empty}
\chapter*{Declaration\markboth{Declaration}{Declaration}}
\thispagestyle{empty}
\noindent {\Large Eidesstattliche Versicherung / Declaration on oath }\\

\noindent Hiermit versichere ich an Eides statt, die vorliegende Dissertationsschrift selbst verfasst und keine anderen als die angegebenen Hilfsmittel und Quellen benutzt zu haben.\\

\noindent Die eingereichte schriftliche Fassung entspricht der auf dem elektronischen Speichermedium.\\

\noindent Die Dissertation wurde in der vorgelegten oder einer {\"a}hnlichen Form nicht schon einmal in einem fr{\"u}heren Promotionsverfahren angenommen oder als ungen{\"u}gend beurteilt.\\


Hamburg, den November 6th 2019

\vspace*{1.5cm}

\rule{0.3\textwidth}{.5pt}\\

Thomas Bourton